The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-07-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_slope_timescale.pdf}
    \caption{\textit{Center:} Abundance tracks in the [Fe/H]-[O/Fe] plane for one-zone models with various DTD parameters. Tracks from models which assume a power-law DTD are in black, with dotted, dashed, and solid curves representing power-law slopes ($\alpha$) of $-0.8$, $-1.1$, and $-1.4$, respectively. Tracks from models which assume an exponential DTD are in blue, with dotted, dashed, and solid curves representing exponential decay timescales ($\tau$) of 1.5 Gyr, 3 Gyr, and 6 Gyr, respectively. In all cases a minimum delay time of 40 Myr is assumed. \textit{Top:} MDFs generated by the one-zone models. \textit{Right:} Distribution of [O/Fe] generated by the one-zone models.}
    \label{fig:onezone-slope-timescale}
    \script{onezone_slope_timescale.py}
\end{figure}

>>>>

\subsection{Nucleosynthetic Yields}
\label{sec:yields}

We use the same yields as in \citet{Johnson2021-Migration}.

\begin{deluxetable}{lll}
    \tablecaption{Nucleosynthetic yields assumed in our simulations.\label{tab:yields}}
    \tablehead{
        \colhead{Source} & \colhead{Element} & \colhead{Yield}
    }
    \startdata
    CCSN    & O     & 0.015     \\
    CCSN    & Fe    & 0.0012    \\
    \hline
    SN Ia   & O     & 0         \\
    SN Ia   & Fe    & 0.00214   \\
    \enddata
\end{deluxetable}

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_powerlaw_slope.pdf}
    \caption{\textit{Center:} Abundance tracks in the [Fe/H]-[O/Fe] plane for one-zone models with a power-law DTD. The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively. In all cases a minimum SN Ia delay time of 40 Myr is assumed. \textit{Top:} Metalliticy distribution functions (MDFs) generated by the one-zone models. \textit{Right:} Distributions of [O/Fe] generated by the one-zone models.}
    \label{fig:onezone-powerlaw-slope}
    \script{onezone_powerlaw_slope.py}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/onezone_exponential_timescale.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with an exponential DTD. The dotted, dashed, and solid curves represent exponential decay timescales $\tau=1.5$ Gyr, 3 Gyr, and 6 Gyr, respectively.}
    \label{fig:onezone-exponential-timescale}
    \script{onezone_exponential_timescale.py}
\end{figure}
